## Note

While all major functionality is available, this package is still in a rather early stage. For example, documentation is mostly missing and the fitting algorithm is implemented inefficiently. Its current purpose is mainly a proof of concept and to enable reachers familiar with R to experiment with Gaussian Process Panel Modeling. The Matlab implementation https://github.com/karchjd/GPPMM is more mature.

The recommended approach to learn about the functionality of the package is currently to closely follow the examples provided. This is described in the following.

## Install

To install the gppmr package, copy the following line into R:
```{r, eval=FALSE}
source('https://raw.githubusercontent.com/karchjd/gppmr/master/tools/gppmrInstall.R')
```


## Examples
The examples for the paper are included as R demos. To see a list of all examples do the following:
```{r}
demo(package='gppmr')
```

To run a particular example, you can do the following. Here, exemplified for 'example1linearModel':
```{r, eval=FALSE}
demo('example1linearModel',package='gppmr')
```

However, the recommended approach is to look at the source directly. To locate the demo folder in which all examples resides on your computer, do the following:
```{r}
system.file("demo", package ="gppmr")
```


